\documentclass[11pt, a4paper]{article}

% Required Packages
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Custom Colors & Link Setup
\definecolor{darkblue}{RGB}{0,0,139}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
    linktoc=page,
}

% Formatting Section Headers
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% Disable Paragraph Indentation
\setlength{\parindent}{0pt}

\begin{document}

% ================= HEADER ================= %
\begin{center}
    {\huge \textbf{Shayan Hussain}} \\ \vspace{4pt}
    Karachi, Pakistan $|$ +92 324 2123466 $|$ \href{mailto:shayanhussain268@gmail.com}{shayanhussain268@gmail.com} \\
    \href{https://portfolio-shayan-hussain.vercel.app/}{portfolio-shayan-hussain.vercel.app} $|$ \href{https://linkedin.com/in/sshayanhussain}{linkedin.com/in/sshayanhussain} $|$ \href{https://github.com/SShayanHussain}{github.com/SShayanHussain}
\end{center}

% ================= OBJECTIVE ================= %
\section*{Professional Summary}
Recent Computer \& Information Systems Engineering graduate with a proven track record of deploying production-grade RAG pipelines, LLM integrations, and MLOps workflows. Seeking an Applied AI role (onsite, remote, or hybrid) to drive scalable, real-world automation through agentic systems and full-stack development.

% ================= EDUCATION ================= %
\section*{Education}
\textbf{NED University of Engineering and Technology} \hfill Karachi, Pakistan \\
Bachelor of Engineering in Computer and Information Systems Engineering \hfill 2022 -- 2026 \\
\textit{CGPA: 3.556 / 4.0} $|$ \textit{Latest SGPA: 3.95 / 4.0}

% ================= SKILLS ================= %
\section*{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Languages:} Python, JavaScript, TypeScript, Java, C, Dart, HTML, CSS, SQL
    \item \textbf{AI \& Machine Learning:} CRAG (Corrective RAG), Ragas, LlamaIndex, RAG Pipelines, LLMs, LangChain, LangGraph, Vector Search, MLOps, TensorFlow, PyTorch, Scikit-learn, OpenCV, YOLO, CNNs, NLP, Transformers, Reinforcement Learning, Pandas, NumPy
    \item \textbf{Cloud \& DevOps:} AWS (EC2, RDS, S3), Docker, Containerization, Nginx, GitHub Actions (CI/CD), GHCR, Vercel, Render
    \item \textbf{Frameworks \& Tools:} FastAPI, Fastify, Next.js (App Router), React, React Flow, Node.js, BullMQ, Celery, Drizzle ORM, TailwindCSS, shadcn/ui, Django, Flask, MERN Stack, Flutter, MCP, FastMCP, n8n, Make.com, UptimeRobot, Git, Vitest, Langfuse
    \item \textbf{Databases \& Storage:} PostgreSQL, pgvector, Redis (Semantic Caching), MySQL, Supabase, SQLite
    \item \textbf{Core Competencies:} Evals-Driven Development, Agentic AI, Multi-Tenancy Architecture, Production Deployment, Computer Vision, Full-Stack AI SaaS, Exactly-Once Processing, Distributed Task Queues
\end{itemize}

% ================= EXPERIENCE ================= %
\section*{Work Experience}

\textbf{Shispare} \hfill Karachi, Pakistan \\
\textit{AI Engineer (Full-time)} \hfill January 2026 -- May 2026
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Designed and deployed a production-grade RAG system for the Stellar LMS platform, successfully automating the generation of assessment questions from PDF course content in a live environment.
    \item Engineered an operational Model Context Protocol (MCP) server for Pipedrive CRM within a 4-person team, automating workflows to eliminate manual effort by 50\% and achieving single-digit second response times for AI agent integrations.
    \item Architected an agentic coding assistant via a VS Code extension, utilizing locally deployed LLMs and a centralized RAG index over Bitbucket/GitHub to ensure enterprise data privacy while accelerating developer workflows.
    \item Optimized and deployed local LLMs, reducing inference and response times by up to 30\% to decrease API dependency and enhance internal tooling efficiency.
\end{itemize}

\textbf{10Pearls} \hfill Remote \\
\textit{MERN Stack Intern} \hfill September 2025 -- November 2025
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Built a scalable, production-ready Notes Application utilizing the MERN stack with robust CRUD functionality, achieving 90\%+ test coverage through rigorous Jest unit testing.
    \item Partnered directly with a senior engineer to execute asynchronous development cycles, managing modular feature branches via GitHub to support seamless remote delivery.
\end{itemize}

\textbf{Softech Digital Group} \hfill Hybrid \\
\textit{Software Development Intern} \hfill September 2025 -- November 2025
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Contributed to the development of a React and FastAPI-based Art DRM Marketplace, successfully integrating PayPal to process secure payment gateways.
    \item Prototyped AI-based virtual Try-On technology integration approaches, validating technical feasibility for commercial product fitting use cases.
\end{itemize}

% ================= PROJECTS ================= %
\section*{Technical Projects}

\textbf{Ringback — Text-First AI Voice Agent Platform} \hfill \textit{2026} \\
\textit{Python, FastAPI, Next.js 14, PostgreSQL, Supabase, Make.com, Docker} $|$ \href{https://ringback-web.vercel.app/}{Live Demo} $|$ \href{https://github.com/SShayanHussain/ringback}{GitHub}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Architected a channel-agnostic AI voice agent core via FastAPI, achieving 100\% task success and a 0\% false-action rate across 14 CI-enforced evaluation scenarios.
    \item Designed deterministic rule-based NLU for reproducible regression testing, with hot-swappable Groq/Gemini integration for production deployment.
    \item Integrated Make.com with HMAC-signed webhooks to automate event routing (bookings, escalations, leads) to Google Calendar and Gmail with sub-second latency.
    \item Deployed a multi-tenant production stack using Vercel, Render, and Supabase, implementing JWT auth, strict tenant-scoped data isolation, and encrypted credential storage.
\end{itemize}

\textbf{Clause — Evals-First Vertical Document Intelligence System} \hfill \textit{2026} \\
\textit{Next.js 16, FastAPI, LangGraph, LlamaIndex, pgvector, Supabase, Ragas} $|$ \href{https://clause-beige.vercel.app/}{Live Demo} $|$ \href{https://github.com/SShayanHussain/clause}{GitHub}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Architected a Corrective RAG (CRAG) legal contract engine using LangGraph and FastAPI, incorporating multi-hop reasoning and a self-critic node to achieve >95\% faithfulness and eliminate untraceable hallucinations.
    \item Pioneered an evals-first methodology via Ragas, gating architectural changes behind an ablation table to drive a 40\% increase in multi-hop accuracy compared to base RAG baselines.
    \item Engineered a structure-aware ingestion pipeline to \textit{pgvector}, linking embeddings to exact hierarchical clause IDs (e.g., 8.1a) to guarantee 100\% citation precision and data provenance.
    \item Developed a Next.js 16 split-view UI featuring verified citation chips that auto-scroll to the exact source text, ensuring dynamic abstention policies when retrieval fails.
\end{itemize}

\textbf{Consensus — Supervisor-Orchestrated Multi-Agent Platform} \hfill \textit{2026} \\
\textit{Next.js 14, FastAPI, Python, LangGraph, Redis, PostgreSQL, FastMCP, Docker} $|$ \href{https://consensus-ai-saas.vercel.app/}{Live Demo} $|$ \href{https://github.com/SShayanHussain/consensus}{GitHub}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Developed a stateful, supervisor-orchestrated multi-agent system using LangGraph and FastAPI, managing specialized agents (Researcher, Analyst, Writer) and enforcing a budget ceiling of \$1.50 per run and a 15-step loop ceiling.
    \item Engineered a robust Human-in-the-Loop (HITL) gate that halts graph execution for consequential actions, serializing state to PostgreSQL with sub-50ms latency and resuming via Redis job queues.
    \item Integrated Langfuse for execution tracing, and built an independent, append-only PostgreSQL audit log guaranteeing 100\% traceability of all agent tool invocations and user approvals.
    \item Created a Next.js console displaying real-time agent run status, workspace-level plan limits (50 runs/mo), and a workflow approval dashboard.
\end{itemize}

\textbf{Flowlet — AI-Native Workflow Automation Platform} \hfill \textit{2026} \\
\textit{Next.js 14, Fastify, PostgreSQL, BullMQ, Redis, React Flow, Docker} $|$ \href{http://flowlet-automate.vercel.app/}{Live Demo} $|$ \href{https://github.com/SShayanHussain/flowlet}{GitHub}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Architected a distributed, multi-tenant AI workflow automation engine utilizing Next.js, Fastify, and BullMQ, enabling users to visually compose complex \textit{trigger $\rightarrow$ AI-step $\rightarrow$ branch} pipelines.
    \item Engineered a highly concurrent job execution worker pool featuring 3-layer idempotency and crash-safe fairness leases, guaranteeing exactly-once execution and maintaining a flat $\sim$20ms p95 enqueue latency under 500+ concurrent burst loads.
    \item Implemented robust backend hardening, including Nginx edge rate-limiting (50 req/s), per-workspace LLM cost tracking, and an AI output cache that eliminated 100\% of redundant API token costs for duplicate inputs.
    \item Validated system reliability through an automated load-testing artifact, achieving 96 req/s sustained throughput and seamlessly draining 500 concurrent triggers in under 14 seconds with zero dropped runs or double-executions.
\end{itemize}

\textbf{Deflekt — Multi-Tenant AI Support Deflection SaaS} \hfill \textit{2026} \\
\textit{AWS EC2/RDS, Next.js 14, FastAPI, pgvector, Redis, Celery, Docker} $|$ \href{http://54.208.178.218/}{Live Demo} $|$ \href{https://github.com/SShayanHussain/deflekt}{GitHub}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Architected a multi-tenant RAG platform using Next.js 14, Python FastAPI, PostgreSQL (pgvector), and Redis, reducing repetitive support ticket volume by 70\% with cited, grounded answers.
    \item Engineered a sub-18ms Redis semantic cache cutting duplicate LLM query latency by 98.5\% and scaled single-instance AWS EC2 throughput to 150+ req/sec (cached) and 45+ req/sec (streaming RAG), supporting 10,000+ daily active users.
    \item Deployed an async Celery worker queue processing ~1,200 words/sec for document ingestion and built an automated CI/CD pipeline on AWS EC2/RDS with an LLM-as-a-Judge eval harness gating builds on >80\% Faithfulness precision.
    \item Enforced strict database-level multi-tenancy isolation and an automated confidence gate (<0.72) that escalates low-confidence queries to human support with <0.8\% hallucination rate.
\end{itemize}

\textbf{RoboComm: Smart Interactive Campus Robot} \hfill \textit{2025 -- Present}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Built an autonomous campus assistant using a custom ESP32 chassis integrated with an MPU6050 (heading estimation) and HC-SR04 (obstacle detection), achieving a navigation accuracy of 85\%.
    \item Deployed real-time YOLO object detection maintaining 25--30 FPS and integrated the Gemini API for natural language STT/TTS interaction, enabling voice-driven campus navigation.
\end{itemize}

\textbf{Voice-Enabled Booking Automation System} \hfill \textit{2026}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Architected a zero-touch conversational agent utilizing Make.com workflows to orchestrate Calendly, Google Calendar, and OpenAI APIs, streamlining the booking lifecycle to a sub-5-minute process and successfully processing 100+ automated user interactions.
\end{itemize}

\textbf{Anomaly Detector Computer Vision Pipeline} \hfill \textit{2026}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Developed an end-to-end MLOps pipeline (hand-annotating 1,500 images via CVAT and augmenting via Roboflow) to train an RT-DETR-L model with a frozen backbone, achieving 88\% accuracy and a peak mAP of 0.650 for anomaly detection on unseen datasets.
\end{itemize}

\textbf{Remote Work Productivity Tracker} \hfill \textit{2026}
\begin{itemize}[leftmargin=0.25in, itemsep=2pt]
    \item Trained a behavioral classification model on a custom, annotated screen-recording dataset of 1,000 hours to track verified work hours with 80\% accuracy, building a real-time Next.js/Node.js analytics dashboard for administrative oversight.
\end{itemize}

\end{document}
